Ecuador Elevation

### 2022-10-12 code/L0/L0_Ecuador_elevation.Rmd
change package used to geodata Still getting an error and can't download data (connection error)

# Install and load required packages
```{r}
library(elevatr)
library(sf)
library(raster)
```
# Take location coordinates and convert to sf object
```{r}
#x= long, y = lat
ecuador <- data.frame(x = -79.3666965, y = -1.3397668) %>%
  st_as_sf(coords = c("x", "y"), crs = 4326)
```

```{r}
elevation <- get_elev_raster(ecuador, z = 9)
```

>>>>

# Install and load required packages
```{r}
library(geodata)
```

```{r}
ecuador_outline <- gadm(country = "ECU", level=1, path = data_path, version="latest", resolution=1)

```

# Download elevation data for Ecuador
```{r}
ecuador <- elevation_30s(country = "ECU", path = data_path)
ecuador
```
